Realizing temporal graphs from fastest travel times

### 2023-05-01 TGR Extended - New paper/Realizing TG - extended.tex
Changes Monday 1st of May

\begin{figure}[t]
	\noindent
	\makebox[\textwidth]{
		\centering
\begin{tikzpicture}%[xscale=2]

@@

    %% edges between x3 gadget and v,c1
    %x3 is FALSE
    %x3 to clause
	\draw (x3t) to node[timelabel,pos=0.75] {$1$} (c1);
    %x3 gadget
	\draw (x3t) to node[timelabel] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
	\draw (x3f) to [out=100,in=330] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
    \draw (x3t) to node[timelabel, pos=0.5] {$1$} (x3) to node[timelabel, pos=0.5] {$3$} (x3f);

    %%% edges between x4 gadget and v,c2
    %x4 is false
    %x4 to clause
	\draw (x4t) to node[timelabel,pos=0.75] {$1$} (c2);
    %x4 gadget
	\draw (x4t) to [out=90,in=340] node[timelabel] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
	\draw (x4f) to [out=90,in=360] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
    \draw (x4t) to node[timelabel, pos=0.5] {$1$} (x4) to node[timelabel, pos=0.5] {$3$} (x4f);

@@

\bibliography{../bibliography}	
\end{document}

>>>>

\begin{figure}[hbt]
	\noindent
	\makebox[\textwidth]{
		\centering
\begin{tikzpicture}%[xscale=2]

@@

    %% edges between x3 gadget and v,c1
    %x3 is FALSE
    %x3 to clause
	\draw (x3t) to node[timelabel,pos=0.75] {$1$} (c1);
    %x3 gadget
	\draw (x3t) to node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
	\draw (x3f) to [out=100,in=330] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
    \draw (x3t) to node[timelabel, pos=0.5] {$1$} (x3) to node[timelabel, pos=0.5] {$3$} (x3f);

    %%% edges between x4 gadget and v,c2
    %x4 is false
    %x4 to clause
	\draw (x4t) to node[timelabel,pos=0.75] {$1$} (c2);
    %x4 gadget
	\draw (x4t) to [out=90,in=340] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
	\draw (x4f) to [out=90,in=360] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
    \draw (x4t) to node[timelabel, pos=0.5] {$1$} (x4) to node[timelabel, pos=0.5] {$3$} (x4f);

@@

\bibliography{bibliography}	
\end{document}
